\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach

### 2022-03-11 presentations/presentationBoston/presentationBoston.Rmd
Adds new table

Religion Debiasing  | MAC (distance)
------------- | -------------
Biased        | 0.859
Hard Debiased | 0.934
Soft Debiased ($\lambda$ = 0.2) | 0.894

>>>>

Category | Biased | Hard Debiased | Soft Debiased | Diff |
-------| ------| -------| ----- | --------
Religion | 0.859 | 0.934 | 0.894| 0.075 |
Race | 0.892 | 0.925| 0.985 | 0.033 |
Gender | 0.623 | 0.700 | 0.747 | 0.077 |
